---
title: "Studying African Farmer-Led Irrigation"
format: html
editor: visual
---

## Quarto

```{r setup, include=FALSE, echo = FALSE,message=FALSE}
library(DBI)
library(duckdb)
library(tidyverse)
library(janitor)
```

```{r}
rm(list = ls())
dbDisconnect(con)
```
```{r}
con <- dbConnect(duckdb(),"../DATA/tidytuesday.duckdb")
```
```{r}
data <- dbGetQuery(con,"SELECT * FROM safi_data ")
dbDisconnect(con)
```
```{r}
# data <- data %>%
  separate_rows(items_owned, sep = ";")

# Splitting the items_owned variable into new rows and trim spaces
data <- data %>%
  separate_rows(items_owned, sep = ";") %>%
  mutate(items_owned = str_trim(items_owned))


data <- data %>%
  separate_rows(months_lack_food, sep = ";")

# Splitting the items_owned variable into new rows and trim spaces
data <- data %>%
  separate_rows(items_owned, sep = ";") %>%
  mutate(items_owned = str_trim(months_lack_food))

```


```{r}


# Summary statistics
summary(data)

# Count the number of missing values in each variable
colSums(is.na(data))

# Exploring individual variables

# Village
table(data$village)

# Interview date
table(data$interview_date)

# Number of members in the household
summary(data$no_membrs)

# Number of years living in the village
summary(data$years_liv)

# Type of walls the house has
table(data$respondent_wall_type)

# Number of rooms in the main house used for sleeping
summary(data$rooms)

# Membership of an irrigation association
table(data$memb_assoc)

# Affected by conflicts with other irrigators
table(data$affect_conflicts)

# Livestock count
summary(data$liv_count)

# Items owned by the household
table(data$items_owned)

# Number of meals per day
summary(data$no_meals)

# Months lacking food
table(data$months_lack_food)

# Instance ID (can be skipped for analysis)
```

# Bar plot of village distribution

```{r}
ggplot(data, aes(x = village)) +
  geom_bar() +
  xlab("Village") +
  ylab("Count")

```

# Histogram of number of members in the household

```{r}

ggplot(data, aes(x = no_membrs)) +
  geom_histogram(binwidth = 1) +
  xlab("Number of Members") +
  ylab("Count")

```

# Boxplot of years living in the village

```{r}
ggplot(data, aes(y = years_liv)) +
  geom_boxplot() +
  ylab("Years Living in the Village")

```

# Bar plot of wall types

```{r}
ggplot(data, aes(x = respondent_wall_type)) +
  geom_bar() +
  xlab("Wall Type") +
  ylab("Count")

```

# Histogram of number of rooms

```{r}
ggplot(data, aes(x = rooms)) +
  geom_histogram(binwidth = 1) +
  xlab("Number of Rooms") +
  ylab("Count")

```

# Bar plot of membership of an irrigation association

```{r}
ggplot(data, aes(x = memb_assoc)) +
  geom_bar() +
  xlab("Membership of Irrigation Association") +
  ylab("Count")

```

# Bar plot of conflicts affecting irrigators

```{r}
ggplot(data, aes(x = affect_conflicts)) +
  geom_bar() +
  xlab("Affected by Conflicts with Irrigators") +
  ylab("Count")

```

# Histogram of livestock count

```{r}
ggplot(data, aes(x = liv_count)) +
  geom_histogram(binwidth = 1) +
  xlab("Livestock Count") +
  ylab("Count")

```

# Bar plot of items owned

```{r}
ggplot(data, aes(x = items_owned)) +
  geom_bar() +
  xlab("Items Owned") +
  ylab("Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

# Histogram of number of meals per day

```{r}
ggplot(data, aes(x = no_meals)) +
  geom_histogram(binwidth = 1) +
  xlab("Number of Meals per Day") +
  ylab("Count")

```

# Bar plot of months lacking food

```{r}
ggplot(data, aes(x = months_lack_food)) +
  geom_bar() +
  xlab("Months Lacking Food") +
  ylab("Count")

```

